The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-18 paper/ms.tex
minor

The TESS mission \citep{ricker_transiting_2015} holds the promise to
deliver the most homogeneous and comprehensive cluster photometric
survey in history.  Based on the cluster membership database of
\citet{Kharchenko_et_al_2013} and the TESS apparent magnitude
calculator of \citet{Jaffe_Barclay_2017}, we estimated that $\approx
2\times10^5$ cluster members brighter than $T=16$ will be observed in
the full-frame images over the first two years of TESS observations.
The actual number may be even larger, as cluster membership catalogs
are by no means complete, even at these relatively bright magnitudes
(CITE recent Gaia discoveries of nearby OCs).

@@

\acknowledgements
L.G.B.\ gladly acknowledges helpful discussions with
..., and is
grateful to the people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks ...
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	2MASS \citep{skrutskie_tmass_2006},
    DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{astroquery.gaia}
  \texttt{astroquery.simbad}
  \texttt{astroquery.mast}
  \texttt{astroquery.nasaexopanetarchive}  
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TagSpaces} (CITE),
  \texttt{tesscut} \citep{brasseur_astrocut_2019}
}

>>>>

The TESS mission \citep{ricker_transiting_2015} holds the promise to
deliver the most homogeneous and comprehensive cluster photometric
survey in history.  Based on the cluster membership database of
\citet{Kharchenko_et_al_2013} and the TESS apparent magnitude
calculator of \citet{Jaffe_Barclay_2017}, we estimated that $\approx
2\times10^5$ cluster members brighter than $T=16$ will be observed in
the full-frame images over the first two years of TESS observations.
The actual number may be even larger, as cluster membership catalogs
are by no means complete, even at these relatively bright magnitudes.
For example, using Gaia-DR2 \citet{cantat-gaudin_newOCs_2019}
discovered a few tens of previously undetected open clusters in
the direction of Perseus. Earlier, \citet{cantat-gaudin_gaia_2018}
fortuitously discovered 60 open clusters as well; however a
homogeneous all-sky search with Gaia data has yet to be performed.

@@

\acknowledgements
L.G.B.\ gladly acknowledges helpful discussions with
C Huang, M Soares-Furtado, ...
..., and is
grateful to the people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks ...
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	2MASS \citep{skrutskie_tmass_2006},
    DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{astroquery.gaia}
  \texttt{astroquery.simbad}
  \texttt{astroquery.mast}
  \texttt{astroquery.nasaexopanetarchive}  
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TagSpaces} (CITE),
  \texttt{tesscut} \citep{brasseur_astrocut_2019}
}
